Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-13 secondPaper/accordionComplexSurfaces.tex

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
We note that our dissections are always cellular, while those found in \cite{BaurCoelhoSimoes} can be arbitrary.
Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.

>>>>

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
We note that our dissections are always cellular, while those found in \cite{BaurCoelhoSimoes} can be arbitrary.
Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich, LekiliPolishchuk}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.
